---
title: "Initial Comparisons"
author: "Sean Lucey"
date: "2/03/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table); library(here); library(comlandr); library(ggplot2)
```

These are some initial comparisons between the 2019 AA and CAMS tables.  Data were pulled using the `get_comland_raw_data` function from the R package `comlandr` created and maintained by the Ecosystem Dynamics and Assessment Branch (EDAB) of the Northeast Fisheries Science Center (NEFSC).

```{r Data Pull}
load(file = here('data-raw', 'CAMS_2019.RData'))
load(file = here('data-raw', 'AA_2019.RData'))
#move data out to main object
aa <- aa$comland
```

First some simple metrics
```{r}
nrow(cams)
nrow(aa)
```

Total landings
```{r}
cams[, sum(SPPLIVMT)]
aa[, sum(SPPLIVMT)]
```

Landings that are missing area
```{r}
cams[AREA == 0, sum(SPPLIVMT)]
aa[AREA == 0, sum(SPPLIVMT)]
```

As percentage
```{r}
cams[AREA == 0, sum(SPPLIVMT)] / cams[, sum(SPPLIVMT)]
aa[AREA == 0, sum(SPPLIVMT)] / aa[, sum(SPPLIVMT)]
```

Now to run the scripts for the SOE.  First assign landings to an EPU then aggregate landings by SOE groups.

```{r}
load(here('data-raw', 'SOE_species_list.RData'))

#AA
#Assign areas based on mskeyAreas
aa <- aggregate_area(aa, userAreas = comlandr::mskeyAreas, areaDescription = 'EPU',
                     propDescription = 'MeanProp')

#Aggregate by EBFM codes
aa.agg <- merge(aa, unique(species[!is.na(NESPP3), list(NESPP3, SOE.20, Fed.Managed)]), 
                by = 'NESPP3', all.x = T)

#Fix NA codes
aa.agg[is.na(SOE.20), SOE.20 := 'Other']

#Sum Landings
aa.land <- aa.agg[, sum(SPPLIVMT), by = c('YEAR', 'EPU', 'SOE.20', 'Fed.Managed')]
aa.land[, Total := sum(V1), by = c('YEAR', 'EPU', 'SOE.20')]
aa.land[, Prop.managed := V1 / Total]
setnames(aa.land, 'V1', 'SPPLIVMT')

aa.land
```

```{r}
#CAMS
#Assign areas based on mskeyAreas
cams <- aggregate_area(cams, userAreas = comlandr::mskeyAreas, areaDescription = 'EPU',
                       propDescription = 'MeanProp')

#Aggregate by EBFM codes
cams.agg <- merge(cams, unique(species[!is.na(NESPP3), 
                                       list(NESPP3, SOE.20, Fed.Managed)]),
                  by = 'NESPP3', all.x = T)

#Fix NA codes
cams.agg[is.na(SOE.20), SOE.20 := 'Other']

#Sum Landings
cams.land <- cams.agg[, sum(SPPLIVMT), by = c('YEAR', 'EPU', 'SOE.20', 'Fed.Managed')]
cams.land[, Total := sum(V1), by = c('YEAR', 'EPU', 'SOE.20')]
cams.land[, Prop.managed := V1 / Total]
setnames(cams.land, 'V1', 'SPPLIVMT')

cams.land

```

Graphical differences

```{r}
#Merge landings
all <- merge(aa.land, cams.land, by = c('YEAR', 'EPU', 'SOE.20', 'Fed.Managed'))
setnames(all, c('SPPLIVMT.x', 'Total.x', 'Prop.managed.x', 
                'SPPLIVMT.y', 'Total.y', 'Prop.managed.y'),
         c('AA.SPPLIVMT',   'AA.Total',   'AA.Prop.managed',
           'CAMS.SPPLIVMT', 'CAMS.Total', 'CAMS.Prop.managed'))

tot.land <- unique(all[, list(YEAR, EPU, SOE.20, AA.Total, CAMS.Total)], 
                   by = c('YEAR', 'EPU', 'SOE.20'))

#Put in long form
tot.land.long <- data.table::melt(tot.land, id.vars = c('YEAR', 'EPU', 'SOE.20'))

#Plot as a barplot
land.bar <- ggplot(data = tot.land.long, 
                   aes(SOE.20, value, fill = variable)) +
    geom_bar(stat = "identity", position = 'dodge') +
    facet_grid(rows = 'EPU', scales = "free")

plot(land.bar)


```
