---
title: "Initial Comparisons"
author: "Sean Lucey"
date: "1/18/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table); library(here)
```

These are some initial comparisons between the 2019 AA and CAMS tables.  Data were pulled using the `get_comland_raw_data` function from the R package `comlandr` created and maintained by the Ecosystem Dynamics and Assessment Branch (EDAB) of the Northeast Fisheries Science Center (NEFSC).

```{r Data Pull}
load(file = here('data-raw', 'CAMS_2019.RData'))
load(file = here('data-raw', 'AA_2019.RData'))
#move data out to main object
aa <- aa$comland
```

First some simple metrics
```{r}
nrow(cams)
nrow(aa)
```

Total landings
```{r}
cams[, sum(SPPLIVMT)]
aa[, sum(SPPLIVMT)]
```

Landings that are missing area
```{r}
cams[AREA == 0, sum(SPPLIVMT)]
aa[AREA == 0, sum(SPPLIVMT)]
```

As percentage
```{r}
cams[AREA == 0, sum(SPPLIVMT)] / cams[, sum(SPPLIVMT)]
aa[AREA == 0, sum(SPPLIVMT)] / aa[, sum(SPPLIVMT)]
```
